Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2020-01-27 analysis/paper/paper.Rmd
turning to continue editing the discussion section

By standardizing standard deviation in each data set, the coefficients of variation values allows us to directly compare variation in samples measured with different units or means. We take this as our measurement of standardisation in vessel shape: lower CV values reflect higher standardisation, and thus increased craft specialisation in the community. To answer the question of whether CV values for vessels samples across our three occupational phases are significantly different or not, we used the the Modified signed-likelihood ratio (MSLR) test for equality of CVs [@Krishnamoorthy2014]. While previous work has used the @Feltz1996 Asymptotic test for the equality of coefficients of variation from k populations, we prefer the MSLR test as a more recent development with lower rates of type I error, better performance with uneven sample numbers, and more power across a range of conditions [@Krishnamoorthy2014].

>>>>

By standardizing standard deviation in each data set, the coefficients of variation values allows us to directly compare variation in samples measured with different units or means. We take this as our measurement of standardisation in vessel shape: lower CV values reflect higher standardisation, and thus increased craft specialisation in the community. To answer the question of whether CV values for vessels samples across our three occupational phases are significantly different or not, we used the the Modified signed-likelihood ratio (MSLR) test for equality of CVs [@Krishnamoorthy2014]. While previous work has used the @Feltz1996 asymptotic test for the equality of coefficients of variation from k populations <!-- add citation to archaeology papers using the asymptotic test  -->, we prefer the MSLR test as a more recent development with lower rates of type I error, better performance with uneven sample numbers, and more power across a range of conditions [@Krishnamoorthy2014].
